%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
                                                          % if you need a4paper
%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                          % paper

%\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
%\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

\usepackage[pdftex]{graphicx}
\graphicspath{{resources/}}

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xspace}  
\usepackage{cite}  

\newcommand{\diaspec}{Dia\-Spec\xspace}
\newcommand{\ie}{\emph{i.e.,}}
\newcommand{\eg}{\emph{e.g.,}}
\newcommand{\etc}{\emph{etc}}
\newcommand{\etal}{\emph{et al.}}

\title{Using the \diaspec{} design language and compiler to develop
  robotics systems}

\author{%
  \parbox{2.5 in}{\centering Damien Cassou\\
    Software Architecture Group, HPI\\
    University of Potsdam, Germany\\%
    {\tt\small damien.cassou@hpi.uni-potsdam.de}}
%  \hspace*{ 0.1 in}
  \parbox{2.5 in}{ \centering Serge Stinckwich\\
UMMISCO, UMI 209\\IRD/IFI/Vietnam National University
    {\tt\small serge.stinckwich@ird.fr}}
%  \hspace*{ 0.1 in}
  \parbox{2.5 in}{ \centering Pierrick Koch\\
CNRS, UMR 6072 GREYC\\ F-14032 Caen, France\\
    {\tt\small pierrick.koch@unicaen.fr}}
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

  A Sense/Compute/Control (SCC) application is one that interacts with
  the physical environment. Such applications are pervasive in domains
  such as building automation, assisted living, and autonomic
  computing. Developing an SCC application is complex because the
  implementation must address both the interaction with the
  environment and the application logic, because any evolution in the
  environment must be reflected in the implementation of the
  application, and because correctness is essential, as effects on the
  physical environment can have irreversible consequences.

  The SCC architectural pattern and the \diaspec{} design language
  propose a framework to guide the design of such applications. From a
  design description in \diaspec{}, the \diaspec{} compiler is capable
  of generating a programming framework that guide the developer in
  implementing the design and that provide runtime support. In this
  paper, we report on an experiment using \diaspec{} (both the design
  language and compiler) to develop a robotics application. We present
  how using \diaspec{} has enabled us to develop a robotics
  application that can be adapted easily.

\end{abstract}

\input{introduction}
\input{designing}
\label{sec:implementing}
\label{sec:discussing}
\label{sec:related}
\label{sec:conclusion}

\bibliographystyle{plain}
\bibliography{dslrob}

\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% TeX-PDF-mode: t
%%% coding: utf-8
%%% ispell-local-dictionary: "english"
%%% End:
